\section{Questions}
\label{sec:questions}
The advice and expert knowledge within F-secure is asked in particular on the following questions:
\begin{enumerate}
    \item Would you perhaps be able to give us an approximation on the $V,W,X,Y,Z$ percentages of cyberattacks as displayed in \cref{fig:protocol_scope}? 
    \begin{enumerate}
        \item Note, we will have to do our own due-diligence on this, however, as a first indicator/ballpark estimate, your perspective would significantly move us forward in assessing the (potential) real-world impact of the proposed protocol. 
        \item Are there relevant attack strategies that we omitted? (That are perhaps (indirectly) suitable for the proposed protocol).
    \end{enumerate}
    \item Based on your experience, would you expect the protocol to be of value in real-world applications?
    \begin{enumerate}
        \item (If not), which bottlenecks do you identify?
    \end{enumerate}
    \item Would you consider a talk at Blackhat feasible (assuming the work is done well), with as topic: a presentation of the protocol (specification) with/without working implementation?
    \begin{enumerate}
        \item Note, understand you do not have an crystal ball, however, perhaps your team has more experience into typical Blackhat submission topics and trends, than us.
    \end{enumerate}
    \item Are there perspectives that you would like to share? Did we miss any angles/relevant factors? Is there any advice you could give us, or research-directions that may be relevant in this endeavour?
\end{enumerate}