\section{Planning}
\label{sec:planning}
This section summarises the information required to generate a planning towards a Call for Papers submission for the \textit{Policy Track} of the Blackhat 2022 USA submission.


\subsection{Schedule}
The 2022 Blackhat (USA) edition takes place on 2022-08-06 to 2022-08-11. Even though the call for papers is not yet open, one can develop a planning analog to the call for papers for the 2021 Blackhat USA edition. For that conference, the dates were specified as:\\
Source: \url{https://www.blackhat.com/us-21/call-for-papers.html}
\begin{itemize}
	\item Call for Papers Opened: February 2, 2021
	\item Call for Papers Closed: April 10, 2021
	\item Notification to Submitters: end of May, 2021
	\item Event Dates: July 31 - August 5, 2021
\end{itemize}
Hence, shifting the planning with one week, since the 2022 edition will occur one week later:
\begin{itemize}
	\item Call for Papers Opened: February 9, 2021
	\item Call for Papers Closed: April 17, 2021
	\item Notification to Submitters: end of May, 2021
	\item Event Dates: August 06 - August 11, 2022
\end{itemize}

\subsection{Deliverables}
To create a succesfull submission to the Blackhat 2022 (USA) edition, the following deliverables are required:
\begin{enumerate}
	\item A track specification.
	\begin{itemize}
		\item Source: \url{https://www.blackhat.com/html/tracks.html}
	\end{itemize}
	
	\item \textit{Assumed:} Abstract specification
	\begin{itemize}
		\item Source: \url{https://i.blackhat.com/docs/cfp-sample-submissions.pdf}
	\end{itemize}
	
	\item \textit{Assumed:} Presentation Outline
	\begin{itemize}
		\item Source: \url{https://i.blackhat.com/docs/cfp-sample-submissions.pdf}
	\end{itemize}

	\item \textit{Assumed:} Attendee Takeaways
	\begin{itemize}
		\item Source: \url{https://i.blackhat.com/docs/cfp-sample-submissions.pdf}
	\end{itemize}

	\item \textit{Assumed:} Why Black Hat motivation.
	\begin{itemize}
		\item Source: \url{https://i.blackhat.com/docs/cfp-sample-submissions.pdf}
	\end{itemize}
	
	\item \textit{Assumed:} Presentation slides.
	\begin{itemize}
		\item Source: Imagination.
	\end{itemize}
\end{enumerate}


\subsubsection{Submission Requirements (ASIA)}
The following Blackhat submission requirements are specified for the ASIA event:\\
Source: \url{https://www.blackhat.com/call-for-papers.html}
\begin{enumerate}
	\item Submissions may only be entered by researchers/speakers (no submissions from PR firms/marketing representatives).
	\item Black Hat does not accept product or vendor-related pitches. Black Hat will disqualify any product or vendor pitch.
	\item Submissions must clearly detail the concepts, ideas, findings, and solutions a researcher or speaking team plans to present.
	\item Submissions that highlight new research, tools, vulnerabilities, etc. will be given priority.
	\item Submissions that include White Papers are highly encouraged and will also be given priority.
	\item Black Hat will disqualify incomplete submissions; complete your submission in its entirety.
	\item Individuals may submit more than one proposal, but each proposal must be submitted via a separate submission form.
	\item Each submission must include detailed biographies of the proposed speaking team.
	\item Submitters will be contacted directly if Review Board members have any questions about a submission.
\end{enumerate}

\subsubsection{Tailoring Submission}
Suggested resources to tailor the submission to maximise acceptance probability:\\
Source: the recommendation section of: \url{https://asia-briefings-cfp.blackhat.com/}.
\begin{itemize}
	\item Example submissions: \url{https://i.blackhat.com/docs/cfp-sample-submissions.pdf}
	\item Tips: \url{https://insinuator.net/2017/04/some-quick-tips-for-submitting-a-talk-to-black-hat-or-troopers/}
	\item Acceptance: \url{https://www.helpnetsecurity.com/2016/03/30/how-to-get-your-talk-accepted-at-black-hat/}
	\item Tips: \url{https://hexsec.blogspot.com/2012/12/create-good-security-cfp-responses.html}
	\item Pitfall avoidance: \url{https://research.kudelskisecurity.com/2020/04/02/5-common-cfp-submission-mistakes-for-security-conferences/}
\end{itemize}